\documentclass{resume}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}
\usepackage{multicol}
\usepackage{fontawesome}
\newenvironment{twoitemize}{\begin{multicols}{2}\raggedright\begin{itemize}}{\end{itemize}\end{multicols}}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,filecolor=magenta,urlcolor=blue}
\def\Plus{\texttt{+}}\def\Minus{\texttt{-}}

\name{Mohammad Nurullah Patwary}
\address{
    \faEnvelope~noor.fahim1192@gmail.com \quad
    \faLinkedinSquare~\href{https://www.linkedin.com/in/nurullah-patwary}{linkedin.com/in/nurullah-patwary} \quad
    \faGithub~\href{https://github.com/darkprince92}{github.com/darkprince92}
}
\address{Arlington, Texas, US}

\begin{document}

% ===== SUMMARY =====
\begin{rSection}{Summary}
PhD student in Computer Science (GPA 4.0) at UT Arlington with production experience building
large-scale backend systems, microservices, and event-driven architectures in Java and Python.
Engineered systems serving 100K concurrent users and drove 200$\times$ user acquisition growth.
Brings hands-on AWS, Apache Kafka, API design, and scalability expertise to DoorDash's logistics marketplace.
\end{rSection}

% ===== EXPERIENCE =====
\begin{rSection}{Experience}

\begin{rSubsection}{Agoda}{June 2022 -- July 2023}{Software Engineer}{Bangkok, Thailand}
  \item Engineered backend authentication service for user account management, streamlining workflows
        for millions of end-users, B2B clients, and third-party integrations on Agoda's travel platform.
  \item Identified login breach attack vectors and shipped two-factor authentication validated via A/B
        testing, strengthening account security across the platform's user base.
  \item Improved monitoring and analytics pipelines using ELK Stack to detect and mitigate live login
        attacks in real time, reducing mean time-to-detect security incidents.
\end{rSubsection}

\begin{rSubsection}{Priyo Sys Ltd.}{February 2020 -- May 2022}{Senior Software Engineer}{Dhaka, Bangladesh}
  \item Architected Enterprise HR software with people-data inventory and multi-degree network graph,
        deployed to enterprise clients across Bangladesh.
  \item Extended Django ORM with field-level access control, row-level versioning, and hierarchical
        permissions, eliminating unauthorized data access across all tenants.
  \item Engineered nationwide quiz platform on AWS delivering 50M questions to 100K concurrent users,
        sustaining high availability during peak traffic.
\end{rSubsection}

\begin{rSubsection}{iPay Systems Ltd.}{December 2015 -- December 2019}{Software Engineer}{Dhaka, Bangladesh}
  \item Designed and built backend microservices for a large-scale mobile wallet service processing
        millions of daily transactions for a national fintech platform.
  \item Built on-premise data warehouse with Apache Kafka streaming and event-driven analytics,
        enabling real-time fraud detection and transaction monitoring.
  \item Engineered instant cashback service that scaled daily signups 200$\times$ (150 to 30,000),
        driving a major user acquisition breakthrough.
\end{rSubsection}

\end{rSection}

% ===== SKILLS =====
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{2ex}} l }
Languages      & Java, Python, JavaScript, Kotlin \\
Frameworks     & Spring, Django \\
Databases      & PostgreSQL, Cassandra, Elasticsearch, MongoDB, SQL \\
Cloud \& Infra & AWS, Docker, Apache Kafka, Redis, Ansible \\
Tools          & Git, RabbitMQ, ELK Stack \\
Engineering    & Microservices, API Design, Service-Oriented Architecture, Scalability, CI/CD \\
\end{tabular}
\end{rSection}

% ===== EDUCATION =====
\begin{rSection}{Education}

\begin{rSubsection}{University of Texas at Arlington}{August 2023 -- Present}{PhD in Computer Science}{Arlington, Texas}
  \item Expected graduation: May 2028 \quad CGPA: 4.0
\end{rSubsection}

\begin{rSubsection}{Bangladesh University of Engineering and Technology}{January 2010 -- September 2015}{BS in Computer Science and Engineering}{Dhaka, Bangladesh}
  \item[]
\end{rSubsection}

\end{rSection}

% ===== RESEARCH EXPERIENCE =====
\begin{rSection}{Research Experience}

\begin{rResearch}{University of Texas at Arlington}{May 2024 -- Present}{Graduate Research Assistant}{Arlington, Texas}
  \item Built VS Code language extension for Alloy with syntax highlighting, error reporting, and
        intelligent code completion, improving developer tooling for formal software modeling.
  \item Developed live programming system providing real-time feedback for finite model finders,
        published at FormaliSE 2025 (IEEE).
\end{rResearch}

\end{rSection}

\end{document}
