%------------------------
% Professional Experience
%------------------------
% \newpage

\begin{rSection}{Experiences}
    \begin{rSubsection}{Agoda Services Co., Ltd.}{June 2022 - July 2023}{Software Engineer}{Bangkok, Thailand.}
        \item Engineered backend features for user account management, optimizing authentication workflows for end-users, B2B clients, and third-party integrations.
        \item Investigated login breach patterns and implemented robust two-factor authentication solutions, validated through targeted A/B testing.
        \item Enhanced monitoring and analytics pipelines to detect and mitigate login attacks across segregated zones.
    \end{rSubsection}

    \begin{rSubsection}{Priyo Sys Ltd.}{February 2020 - May 2022}{Senior Software Engineer}{Dhaka, Bangladesh.}
        \item Designed architecture of Enterprise software that featured people data inventory and multi-degree network of data.
        \item Enhanced Django ORM to support field level access control, row-level versioning and hierarchical user-level permissions.
        \item Engineered the infrastructure of nationwide quiz system on AWS and delivered 50M questions to 100K users concurrently.
    \end{rSubsection}

    % \begin{rSubsection}{Craftsmen Ltd.}{January 2020 - February 2020}{Software Engineer II}{Dhaka, Bangladesh.}
    %     \item Developed backend services using AWS lambda, dynamodb, and cloudformation.
    % \end{rSubsection}

    \begin{rSubsection}{iPay Systems Ltd.}{December 2015 - December 2019}{Software Engineer}{Dhaka, Bangladesh.}
        \item Designed and developed backend systems and microservces for \href{https://www.ipay.com.bd/}{iPay Bangladesh} that served large scale wallet service.
        \item Built on-premise data warehouse, data visualization, and automation services for business analytics and log monitoring.
        \item Engineered large scale instant cashback service that boosted user acquisition by 200X (150 to 30000 daily signups).
        \item Built automated user verification service against national ID data and reduced onboarding time from hours to minutes.
    \end{rSubsection}

\end{rSection}